### 2016-12-01 religions_of_the_west/test_02.tex
done with 480

\begin{document}
\section*{Test 2 Review}
\begin{enumerate}
    \item Who is Ahura Mazda? Who is Angra Mainyu?
    \begin{enumerate}
        \item Ahura Mazda
        \begin{itemize}
            \item Creator God in Zoroastrianism
            \item Sole God of the religion
            \item Followers worship his attributes (\textit{Amesha Spentas})
            \item Had evil twin spirit named Angra Mainyu
            \item Truth teller
        \end{itemize}
        \item Angra Mainyu
        \begin{itemize}
            \item Evil counterpart to Ahura Mazda
            \item Can also create things
            \item Lier and deceiver (similar to Satan)
        \end{itemize}
    \end{enumerate}

    \item List some similarities between Zoroastrianism, Christianity, and post-exilic Judaism.
    \begin{itemize}
        \item Central God; Zoroastrianism: Ahura Mazda, Judaism/Christianity: Yahweh
        \item Some sects of Judaism look for Messiah; Christianity has Jesus; Zoroastrianism looked for Saoshyant\
        \item Similar eschatology (final judgment, raising of the dead)
        \item Devil figure (Angra Mainyu/Satan)
    \end{itemize}

    \item Discuss what the church said about Jesus Christ at Nicea and Chalcedon.
    \begin{enumerate}
        \item Nicea
        \begin{itemize}
            \item First ecumenical council of the Church
            \item Needed to establish doctrine to unite Christians
            \item Hosted by Constantine
            \item Athanasius proposed homoousios
            \begin{itemize}
                \item Father and son have same nature but are not the same
                \item Father and son share the same essence.
            \end{itemize}
            \item Trinity idea proposed (later rejected by enlightenment Christians)
        \end{itemize}
        \item Chalcedon
        \begin{itemize}
            \item Council met to settle disputes over Jesus' nature
            \item Greek ideas (God is separate) clashing with Hebrew ideas (God is with humanity)
            \item Leo's Tome: Jesus has two full natures in one person (Orthodox position)
            \item Established Mary's position in the church (Humans < Mary < God)
            \item Roman bishop gains authority at this council
        \end{itemize}
    \end{enumerate}

    \item Describe the evolution of the Papacy.
    \begin{itemize}
        \item Peter considered to be head of Church after Jesus' death
        \item Bishops are established throughout the known world
        \item Chalcedon: Bishop of Rome gains authority in establishing Doctrine
        \item Bishop of Rome becomes authority of the Church (i.e. Pope)
        \item Pope reigns above kings in the middle ages
        \item Church of England splits from the Catholic church over disputes (power of Pope weakened)
        \item Other theologians begin to reject Church's teaching (Martin Luther, John Calvin, etc.) further weakening the Pope's authority
    \end{itemize}

    \item What do Pelagius, Augustine, Erasmus, and Calvin believe about God's sovereignty and human freedon?
    \begin{enumerate}
        \item Pelagius
        \begin{itemize}
            \item Humans have free will
            \item Good deeds will lead you to heaven
            \item Did not believe in God's saving grace
        \end{itemize}
        \item Augustine
        \begin{itemize}
            \item Humans were predestined
            \item God selects certain people to receive his grace
            \item Only those who have been given the grace of God can follow
            \item Works on Earth do not matter
        \end{itemize}
        \item Erasmus
        \begin{itemize}
            \item Grace of God and works lead to salvation
            \item Humans have free will to follow or reject God
            \item Strong focus on working with God
            \item Followed by Catholic church
        \end{itemize}
        \item Calvin
        \begin{itemize}
            \item Humans have no free will
            \item Salvation comes \textbf{only} from the grace of God
            \item Humans are inherently tainted with sin
            \item Some are chosen for heaven; others for hell
            \item Strong emphasis on God's role in human life
        \end{itemize}
    \end{enumerate}

>>>>

\begin{document}
\section*{Test 2 Review}
\begin{enumerate}
    \item Who is Ahura Mazda? Who is Angra Mainyu?
    \begin{enumerate}
        \item Ahura Mazda
        \begin{itemize}
            \item Creator God in Zoroastrianism
            \item Sole God of the religion (Zoroaster believed in one God)
            \item Followers worship his attributes (\textit{Amesha Spentas})
            \item \textit{Amesha Spentas} are good spirits
            \item Had evil twin spirit named Angra Mainyu
            \item Truth teller; truth was very important to Zoroastrianism
        \end{itemize}
        \item Angra Mainyu
        \begin{itemize}
            \item Evil counterpart to Ahura Mazda
            \item created Devas - evil spirits that paralleled \textit{Amesha Spentas}
            \item Attempted to lead Zoroaster astray
            \item Can also create things (evil is a creative force)
            \item Lier and deceiver (similar to Satan)
        \end{itemize}
    \end{enumerate}

    \item List some similarities between Zoroastrianism, Christianity, and post-exile Judaism.
    \begin{itemize}
        \item Central God; Zoroastrianism: Ahura Mazda, Judaism/Christianity: Yahweh
        \item Morality comes from God
        \item Dualism - contest between good an evil (only some sects of Judaism)
        \item Some sects of Judaism look for Messiah; Christianity has Jesus; Zoroastrianism looked for Saoshyant
        \item Coming of God - 1000 years
        \item Similar eschatology (final judgment, raising of the dead)
        \item Devil figure (Angra Mainyu/Satan)
    \end{itemize}

    \item Discuss what the church said about Jesus Christ at Nicea and Chalcedon.
    \begin{enumerate}
        \item Nicea
        \begin{itemize}
            \item First ecumenical council of the Church
            \item Needed to establish doctrine to unite Christians
            \item Hosted by Constantine
            \item Athanasius proposed homoousios
            \begin{itemize}
                \item Nature of Father and Son was very important topic
                \item Father and son have same nature but are not the same
                \item Father and son share the same essence.
            \end{itemize}
            \item Arius: Jesus was separate from God
            \begin{itemize}
                \item Jesus was first creation of God
                \item Jesus was not divine
                \item Rejected by council
            \end{itemize}
            \item Difference between \textit{made} (Arius) and \textit{begotten} (Athanasius)
            \item Trinity idea proposed (later rejected by enlightenment Christians)
        \end{itemize}
        \item Chalcedon
        \begin{itemize}
            \item Council met to settle disputes over Jesus' nature (divine vs. human)
            \item Greek ideas (God is separate) clashing with Hebrew ideas (God is with humanity)
            \item Leo's Tome: Jesus has two full natures in one person (Orthodox position)
            \item Solution proposed by Leo (bishop of Rome)
            \begin{itemize}
                \item Decided Jesus was fully God an fully man
                \item United in one person
                \item Hypostatic union
                \item Gave Leo position of bishop of bishops
            \end{itemize}
            \item Established Mary's position in the church (Humans < Mary < God)
            \item Gave Mary the status of mother of God
        \end{itemize}
    \end{enumerate}

    \item Describe the evolution of the Papacy.
    \begin{itemize}
        \item Peter considered to be head of Church after Jesus' death
        \item Bishops are established throughout the known world
        \item Chalcedon: Bishop of Rome (Leo) gains authority in establishing Doctrine
        \item Gregory the Great is the first recognized Pope
        % \item Innocent III and Gregory VII
        % Innocent III and Gregory VII, nation states, loss of papal power, Vatican I and II
        \item Pope reigns above kings in the middle ages
        \item Holy Roman empire formed by Constantine
        \item Church of England splits from the Catholic church over disputes (power of Pope weakened)
        \item Other theologians begin to reject Church's teaching (Martin Luther, John Calvin, etc.) further weakening the Pope's authority
    \end{itemize}

    \item What do Pelagius, Augustine, Erasmus, and Calvin believe about God's sovereignty and human freedom?
    \begin{enumerate}
        \item Pelagius
        \begin{itemize}
            \item Humans have free will
            \item Good deeds will lead you to heaven
            \item Possibility to serve God
            \item Did not believe in God's saving grace
            \item Reacted against Augustine's teachings
        \end{itemize}
        \item Augustine
        \begin{itemize}
            \item Humans were predestined
            \item Give what you command and command what you will
            \item God selects certain people to receive his grace
            \begin{itemize}
                \item Not all who receive grace are selected (can lose grace)
            \end{itemize}
            \item Human beings are totally depraved (only God's grace can save)
            \item Only those who have been given the grace of God can follow
            \item Works on Earth do not matter
        \end{itemize}
        \item Erasmus
        \begin{itemize}
            \item Grace of God and works lead to salvation
            \item God's grace is far above the good works (do good through God's grace)
            \item Humans have free will to follow or reject God
            \item Strong focus on working with God
            \item Followed by Catholic church
            \item Salvation can be lost/reacquired
        \end{itemize}
        \item Calvin
        \begin{itemize}
            \item Humans have no free will (impunes sovereignty of God)
            \begin{itemize}
                \item Double predestination
                \item Some are chosen for Heaven, others for Hell
            \end{itemize}
            \item Salvation comes \textbf{only} from the grace of God
            \item Humans are inherently tainted with sin (total depravity)
            \begin{itemize}
                \item Every aspect is tainted with iniquity
            \end{itemize}
            \item Strong emphasis on God's role in human life
        \end{itemize}
    \end{enumerate}

### 2016-12-01 software_design/report.tex
done with 480

\begin{document}
\section*{Open Source Project}

@@

@@

Habitica was a very large project; I had never dealt with a project on the magnitude of it before. It was hard to find a bug that I though I could easily fix, much less actually fix it. I ultimately settled on an issue with notifications when purchasing gems.
\begin{quote}
    If you set your language to some of the non-English languages and then go to the Market to buy a gem with gold, you receive two notifications for \texttt{+1 gem}, one in your chosen language and then after a short delay, another one in English:
    \begin{center}
        \includegraphics[scale=0.4]{issue}
    \end{center}
    I've tested a few languages and it happens with only those that have a translation for the \texttt{plusOneGem} text that is different than the English version. For example, it happens with German and French, but not with \texttt{en\_GB}, \texttt{en\MVAt pirate}, or \texttt{zh\_TW} all of which still use the default text: \texttt{"plusOneGem": "+1 Gem"}
\end{quote}
To fix this bug we had to first reproduce it. In the local build for Habitica, there was already a button that would grant the user 10 gems, so I managed to wire it to make a purchase without authentication. The goal was to have the notification fire. Once we reproduced the bug, we needed to locate the place where the notification was being fired twice; it turned out to be in the \texttt{userServices.js} file. The way that Habitica determined whether or not a notification had fired was to compare the contents of the notification that should have fired to the contents of the notification that was being created. If they were the same string value, then the program would not create and fire the second notification; if they were different, however, then the second notification would fire. This was a problem only in languages that had translations for the word \textit{Gem} within Habitica. Since, for example, the French word \textit{Gemme} is not the same as the English translation \textit{Gem}, the notification fired again with \textit{Gem}. To fix this, we simply added a boolean that checked whether or not a notification had already been fired. If it had, then we wouldn't fire the second one; otherwise we would.
\end{document}

>>>>

\begin{document}
\section*{Open Source Project}
\subsection*{Steven Rosendahl}

@@

One of my least favorite things we did this semester was using Angular.js. I've never been a fan of JavaScript in the first place. Not ever knowing what type of Object you have as well as creating Objects on the fly with no schema makes the process of debugging and contributing very difficult. I also dislike frameworks/languages that force you into a certain design pattern; this is one of the reasons I've never been big into iOS programming. With so many JavaScript frameworks out there, Angular.js is a small fish in a big pond. Python was easier to use due to its structure over JavaScript, but much of the open source world is stuck in Python 2.7 whereas the standard is slowly becoming Python 3. This is a little forgivable, since the tools to convert back and forth between the versions are virtually non-existent. This is definitely a problem that could be fixed by the open source world, but it doesn't appear to be a major focus of the majority of projects, especially the scientific ones for which Python is best known. This behavior seems to appeal to the idea that we shouldn't fix what isn't broken, and being a major version number behind doesn't qualify a project as broken, so it is understandable why many large open source projects are not focusing on migration to Python 3.\\

@@

About midway through the semester, I encountered a problem with an application that I was writing for my job. The issue involved an \texttt{SSLException} that was being thrown by versions of Android greater than 6.0. In my search for the answer to why this was happening, I came across the open Android project, which is the open source code for the Android operating system. I knew my issue was arising from Android's native implementation of \texttt{okhttp}, so I spent a while trying to pinpoint my error. I was able to narrow it down to something happening in the handshake, but I couldn't go any further since the stack trace given by LogCat was not specific enough to tell me exactly what step in the handshake process was causing an error. After talking with Dr. Koehl, he recommended that I look into the server logs for the particular server that was hosting the data I needed. When I went to our server manager, he noted that the server was rejecting the certificate that my phone was using to connect; his best suggestion was to look into the source code of the program that was running on the server. He directed me to the appropriate repository, and I began looking through to see if I could find anything about certificate validation and why it would be rejecting the requests made from Android 7.0. Ultimately, I was not able to solve this issue (it's still ongoing). Both the Android OS and the code for the server are open source, so it may be possible that others in the community will be able to fix this issue.\\

Habitica was a very large project; I had never dealt with a project on the magnitude of it before. The first step was to get Habitica installed. Since my computer had just recently been setup with Ubuntu and I'm not a JavaScript developer, I had to install Node.js, Bower, and all of the dependencies. The developer's wiki helped marginally, but I was able to get around many of my troubles by performing the installations essentially backwards. This all had to be run under \texttt{sudo}, since Ubuntu is sensitive to touching anything above the \texttt{{\raise.17ex\hbox{$\scriptstyle\sim$}}/} directory. Others in my group found it a little more difficult and had to resort to using Vagrant/Docker to get things up and running since \texttt{npm} wouldn't play nicely. It was hard to find a bug that I though I could easily fix, much less actually fix it. The first few bugs we looked at involved documenting the Habitica API. Unfortunately, this was near impossible without having used Habitica extensively \textbf{and} having knowledge of the public APIs that were provided. We abandoned that idea an moved on to try and fix an issue with notification not appearing on certain critical hits. I began to look extensively into this issue, but I could not find the place in code where notifications were fired for critical hits. We posted in the developer's chat on Habitica's website, but their suggestions did not help very much. Finally, we found another issue which Matthew promptly claimed. The issue we ultimately settled on involved problems with notifications when purchasing gems.
\begin{quote}
    If you set your language to some of the non-English languages and then go to the Market to buy a gem with gold, you receive two notifications for \texttt{+1 gem}, one in your chosen language and then after a short delay, another one in English:
    \begin{center}
        \includegraphics[scale=0.4]{issue}
    \end{center}
    I've tested a few languages and it happens with only those that have a translation for the \texttt{plusOneGem} text that is different than the English version. For example, it happens with German and French, but not with \texttt{en\_GB}, \texttt{en\MVAt pirate}, or \texttt{zh\_TW} all of which still use the default text: \texttt{"plusOneGem": "+1 Gem"}
\end{quote}
To fix this bug we had to first reproduce it. In the local build for Habitica, there was already a button that would grant the user 10 gems, so I managed to wire it to make a purchase without authentication. The goal was to have the notification fire. Once we reproduced the bug, we needed to locate the place where the notification was being fired twice; it turned out to be in the \texttt{userServices.js} file. The way that Habitica determined whether or not a notification had fired was to compare the contents of the notification that should have fired to the contents of the notification that was being created. If they were the same string value, then the program would not create and fire the second notification; if they were different, however, then the second notification would fire. This was a problem only in languages that had translations for the word \textit{Gem} within Habitica. Since, for example, the French word \textit{Gemme} is not the same as the English translation \textit{Gem}, the notification fired again with \textit{Gem}. To fix this, we simply added a boolean that checked whether or not a notification had already been fired. If it had, then we wouldn't fire the second one; otherwise we would. This appears to have fixed the problem; the only thing left to do now is test that the problem is truly fixed. It might be the case that the second check to see if a notification was fired is necessary; as such, there may be another issue that arises by just ignoring it.\\

Overall, I think open source projects are one of the greatest developments in software engineering. Being able to root though code yourself and fix your own issues is truly a homage to the idea that \textit{if I don't do it, nobody will}. I've come across a lot of bugs in a lot of places, such as wrestling with a seemingly impossible \texttt{SSLException} in Android to the minor annoyance of broken syntax highlighting in Github's Atom with \LaTeX. The open source community is so influential that many companies such as Microsoft, Apple, and Google support and encourage the use and creation of open source software within their own company. Even if I don't have the skills to fix the problem (or the want to fix the problem), chances are someone out there does. That is the true beauty of open source.
\end{document}
